Host Galaxy Association for {\tt DIAObjects}

### 2020-03-26 draft-hostassoc.tex
added DPDD reference to Sec 4.1
fixed typo
minor update to 4.1

This would add unit64[3] and float[3] to the {\tt DIAObject} catalog and to each alert ? a small and worthwhile addition.

@@

\textit{The following text should be posted as a Request For Comments (RFC) in Jira, and at the same time this DMTN should be made official and available.}

>>>>

This would add unit64[3] and float[3] to the {\tt DIAObject} catalog and to each alert, a small and worthwhile addition.

@@

\textit{The following text should be posted as a Request For Comments (RFC) in Jira, and at the same time this DMTN should be made official and available. The RFC would spawn an LSST Change Request on the Data Products Definitions Document (exact proposed changes to DPDD to be written at that time.}
